\documentclass{article}
\usepackage[colorlinks=true]{hyperref}
\usepackage{html}
\usepackage{lscape}
\usepackage{amsmath,amssymb}
\usepackage{threeparttable}

\usepackage{bonmin}


\title{\Bonmin\ Users' Manual}
\author{Pierre Bonami and Jon Lee}


\begin{document}
\maketitle

\input{BOUM_Intro}

\input{BOUM_Obtain}

\input{BOUM_Install}

\input{BOUM_use}

\input{BOUM_options}
%\section{{\Bonmin} output}
%\Bonmin uses a number of optimization tools ({\
%tt Ipopt}, {\tt Cbc}, {\tt Clp}, \ldots) which all have there own output.
%As a consequence the output is very diverse and may be a little difficult to read.\\
%
%The output level for each of the building blocks of \Bonmin can be set through options (see Appendix \ref{app:opt_loglevel})
%Here we briefly describes the output given at the different log level for each of those building blocks.
%\subsection{BB\_log_level}
%This corresponds to the output from the main branch-and-bound process in B-BB, B-QG, B-Hyb
%(this is not available in the B-OA).
%The output here comes from {\tt Cbc}, and each line of output has the prefix {\tt Cbc} and is followed by a number indicating the message type.
%
%\subsection{
\begin{thebibliography}{10}


\bibitem{Betal}
P.~Bonami, A.~W\"achter, L.T.~Biegler, A.R.~Conn, G.~Cornu\'ejols,
I.E.~Grossmann, C.D.~Laird, J.~Lee, A.~Lodi, F.~Margot and
N.~Sawaya.
\newblock An algorithmic framework for convex mixed integer nonlinear programs. IBM Research Report RC23771, Oct. 2005.

\bibitem{Gupta80Nonlinear}
O.K.~Gupta and V.~Ravindran.
\newblock Branch and bound experiments in convex nonlinear integer programming.
\newblock {\em Management Science}, 31:1533--1546, 1985.

%\bibitem{fiacco} A.V.~Fiacco.
%\newblock Introduction to Sensitivity and
%    Stability Analysis in Nonlinear Programming.
%\newblock {\em Academic Press, New
%  York} (1983)

\bibitem{DG}
M.~Duran and I.E.~Grossmann.
\newblock An outer-approximation algorithm for a class of mixed-integer nonlinear programs.
\newblock {\em Mathematical Programming}, 36:307--339, 1986.

\bibitem{FL}
R.~Fletcher and S.~Leyffer.
\newblock Solving mixed integer nonlinear programs by outer approximation.
\newblock {\em Mathematical Programming}, 66:327--349, 1994.

\bibitem{QG}
I.~Quesada and I.E.~Grossmann.
\newblock An {LP/NLP} based branched and bound algorithm for convex {MINLP} optimization problems.
\newblock {\em Computers and Chemical Engineering}, 16:937--947, 1992.

\bibitem{AMPL}
R.~Fourer and D.M.~Gay and B.W.~Kernighan.
\newblock AMPL: A Modeling Language for Mathematical
Programming, Second Edition,
\newblock Duxbury Press Brooks Cole Publishing Co., 2003.

\bibitem{Gay}
D.M.~Gay.
\newblock Writing \texttt{\bf .nl} files.
\newblock Sandia National Laboratories, Technical Report No. 2005-7907P, 2005.

\bibitem{NocedalAdaptive}
J.~Nocedal, A.~W\"achter, and R.~A. Waltz.
\newblock Adaptive Barrier Strategies for Nonlinear Interior Methods.
\newblock Research Report RC 23563, IBM T. J. Watson Research Center, Yorktown, USA (March 2005; revised January 2006)

\bibitem{AndreasIpopt}
A.~W\"achter and L.~T.~Biegler.
\newblock On the Implementation of a Primal-Dual Interior Point Filter Line Search Algorithm for Large-Scale Nonlinear Programming.
\newblock Mathematical Programming 106(1), pp. 25-57, 2006
\end{thebibliography}

\appendix
\section{List of \Bonmin\ options}
\label{sec:optList}
\input{options}


\end{document}
